Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/results.tex
Note from Dan sensei, for RQ2

>>>>

\pick{Note from Dan sensei,}

For cpost effectivness we can state the reduction  percentage in the number of comments that much be checked manually.

 Also point out how much effort manual classification takes and that it is error prone (probably mor so than the automated method!

You cannot, but some estimates are possble

first, human beings have a fairly well known rate of making errors in classification

second, look at the comments in the training set that the method classified differently, especially the unclear.

Review these to see if the method suggested a better classification than was originally made by the assessors

You can consider these errors. Now look at what wans the percent of errors in the training set

This is also an estimate of the human error rate
